---
title: "Week3AssignmentAVR"
author: "AVR"
date: "December 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
##Background
This assignment features the sales of a certain product in the Philippines
(which I can't disclose, sorry) from January to December 2018.  The market is divided
into 8 Market Areas :

- NOL : Northern Luzon
- CEL : Central Luzon
- SOL : South Luzon
- BIC : Bicol
- VIS : Visayas
- NOM : North Mindanao
- SOM : South Mindanao
- MM  : Metro Manila

The plot is 3-dimensional. You can drag the mouse over the figure to rotate the graph.


```{r echo=FALSE, warning=FALSE, message=FALSE }


library(plotly)
library(ggplot2)

setwd("D:/DOST Coursera/Module 9/Week3")
sales_data = read.csv("sales.csv", na.strings=c("", "NA"))


Sales <- as.numeric(sales_data$NEWINSTALL)


plot_ly(sales_data, x=~MONTH, y=~Sales, z=~MARKETAREA, 
        type="scatter3d", color=~factor(MARKETAREA))
```
